The Influence of Connectivity on Dung Beetle Communities

### 2025-07-10 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
added date

---
title: "The Influence of Connectivity on Dung Beetle Communities"
author: "ERIC ESCOBAR-CHENA"
# date: "\\vspace{-1em}"
# header-includes:
 # - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
#  - \usepackage{lineno}
#  - \linenumbers
#  - \usepackage[default]{sourcesanspro}
#  - \usepackage{fancyhdr} # modify header into left, center, right
#  - \pagestyle{fancy} # cues the use of fancy headers
#  - \fancyfoot{} # cues the use of fancy footer
#  - \fancyhead[L]{EEC MS Thesis Draft} # month & year on header left 
#  - \fancyhead[R]{p. \thepage} # name and page on header right
#  - \usepackage{subcaption}
#  - \usepackage{float}
# # # - \fancyfoot[R]{ }
#  - \usepackage{setspace}

header-includes:
  - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \raggedbottom
  - \usepackage{fancyhdr}
  - \pagestyle{plain}
  - \fancyfoot[C]{\thepage}
  - \fancyhead[L]{}
  - \fancyhead[R]{\small{EEC MS Thesis Draft}}
  - \thispagestyle{fancy}
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \usepackage{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
  - \usepackage{indentfirst}
  # - \usepackage{caption}
  # - \captionsetup[figure]{name={Figure 1-},labelsep=period}
  # - \captionsetup[table]{name={Table 1-},labelsep=period}
  - \renewenvironment{abstract}{}{} #suppress the abstract
  - \usepackage{setspace}
  - \setcounter{secnumdepth}{0} # removes numbering from sections and subsections
  - \usepackage{sectsty}\allsectionsfont{\raggedright}
  # - \usepackage{sectsty}\sectionfont{\centering}{\normalfont} # center # headings
  # - \usepackage{sectsty}\subsectionfont{\centering}{\normalfont} # center ## headings
  - \usepackage{sectsty}\subsubsectionfont{\bfseries} # center ## headings
  # - \usepackage{sectsty}\subsubsectionfont{\itshape} # no centering but italic subsu
  # - \usepackage{sectsty}\subsubsectionfont{\centering}{ital} # center ### headings
  # - \usepackage{sectsty}\sectionfont{\centering\color{darkmidnightblue}}

>>>>

---
title: "The Influence of Connectivity on Dung Beetle Communities"
author: "ERIC ESCOBAR-CHENA"
date: "`r format(Sys.time(), '%d %B, %Y')`"
# date: "\\vspace{-1em}"
# header-includes:
 # - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
#  - \usepackage{lineno}
#  - \linenumbers
#  - \usepackage[default]{sourcesanspro}
#  - \usepackage{fancyhdr} # modify header into left, center, right
#  - \pagestyle{fancy} # cues the use of fancy headers
#  - \fancyfoot{} # cues the use of fancy footer
#  - \fancyhead[L]{EEC MS Thesis Draft} # month & year on header left 
#  - \fancyhead[R]{p. \thepage} # name and page on header right
#  - \usepackage{subcaption}
#  - \usepackage{float}
# # # - \fancyfoot[R]{ }
#  - \usepackage{setspace}

header-includes:
  - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \raggedbottom
  - \usepackage{fancyhdr}
  - \pagestyle{plain}
  - \fancyfoot[C]{\thepage}
  - \fancyhead[L]{}
  - \fancyhead[R]{\tiny{EEC MS Thesis Draft (`r format(Sys.time(), '%d %B %Y')`)}}
  - \thispagestyle{fancy}
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \usepackage{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
  - \usepackage{indentfirst}
  # - \usepackage{caption}
  # - \captionsetup[figure]{name={Figure 1-},labelsep=period}
  # - \captionsetup[table]{name={Table 1-},labelsep=period}
  - \renewenvironment{abstract}{}{} #suppress the abstract
  - \usepackage{setspace}
  - \setcounter{secnumdepth}{0} # removes numbering from sections and subsections
  - \usepackage{sectsty}\allsectionsfont{\raggedright}
  # - \usepackage{sectsty}\sectionfont{\centering}{\normalfont} # center # headings
  # - \usepackage{sectsty}\subsectionfont{\centering}{\normalfont} # center ## headings
  - \usepackage{sectsty}\subsubsectionfont{\bfseries} # center ## headings
  # - \usepackage{sectsty}\subsubsectionfont{\itshape} # no centering but italic subsu
  # - \usepackage{sectsty}\subsubsectionfont{\centering}{ital} # center ### headings
  # - \usepackage{sectsty}\sectionfont{\centering\color{darkmidnightblue}}
